---
title: With Latex Header File
output:
  pdf_document:
    fig_caption: yes        
    includes:  
      in_header: my_header.tex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load myData, include=FALSE, echo=FALSE}
load("C:/Users/LPXJGB/Desktop/CHI-2020/CookingProject/fname.RData")
# required libraries
library(knitr)
library(kableExtra)
library(dplyr)
library(ggplot2)
library(ggthemes)
library(htmlTable)
library(scales)
library(formattable)
options(knitr.kable.NA = '')

```

An introduction to results. A description of each one of the results.

### Participants

Here is

```{r, layout="l-body-outset", warning=FALSE, echo=FALSE, message=FALSE}
p_df <- participants.list[, 1:9]

kable(p_df, alig = "l", "latex", caption = "Participants demographics", booktabs = T) %>%
  kable_styling(latex_options ="scale_down")  %>%
   footnote(symbol = ("Notes. p = participant, coo = country of origin, noi = number of inhabitants, nb = non-binary"))
```

### Recipes

Here is

```{r, layout="l-body-outset", warning=FALSE, echo=FALSE, message=FALSE}
recipes_df <- recipe.list[, 1:3]

names(recipes_df)[1:2] <- c("session", "regular")

kable(recipes_df, "latex", alig = "l", caption = "List of recipes", booktabs = T) %>%
  kable_styling(latex_options = c("scale_down",  "hold_position"))
```

### Source of recipes

Here is

```{r, layout="l-body-outset", warning=FALSE, echo=FALSE, message=FALSE}
source_df <- recipe.list[, c(1,4:7)]
# rename data frame column
names(source_df)[names(source_df) == "id"] <- "session"

kable(source_df,  "latex", alig = "l", caption = "Source of recipes", booktabs = T) %>%
  kable_styling(latex_options = c("scale_down",  "hold_position")) %>%
   footnote(symbol = ("Notes. s.time = sugested cooking time in minutes"))
```

### Inventory CPGs

Here is a table of Inventory CPGs

```{r, warning=FALSE, echo=FALSE, message=FALSE}
inv_df <- inventory.list
names(inv_df)[1:2] <- c("participant", "CPGs")

kable(inv_df, alig = "l", "latex", caption = "Inventory CPGs", booktabs = T) %>%
  kable_styling(latex_options = c("hold_position"))
```

### Inventory CPGs

```{r, layout="l-body-outset", warning=FALSE, echo=FALSE, message=FALSE}
inv_df <- inventory.list
names(inv_df)[1:2] <- c("participant", "CPGs")

kable(inv_df, alig = "l", "latex", caption = "Inventory CPGs", booktabs = T) %>%
  kable_styling(latex_options = c("hold_position"))
```

### List of items

```{r, layout="l-body-outset", warning=FALSE, echo=FALSE, message=FALSE}
c_df <- i.lists$c[ ,c(1,3)]
c_dfa <- cbind(c_df[1:51, ], c_df[52:102, ], c_df[103:153, ])

kable(c_dfa, "latex", alig = "l",  caption = "List of CPGs", booktabs = T) %>%
  kable_styling(bootstrap_options = c("condendsed"), latex_options = c("hold_position", "scale_down"))

u_df <- i.lists$u[ ,c(1,3)]
u_dfa <- cbind(u_df[1:28, ], u_df[29:56, ], u_df[57:84, ])

kable(u_dfa, "latex", alig = "l",  caption = "List of utensils", booktabs = T) %>%
  kable_styling(latex_options = c("hold_position", "scale_down"))

e_df <- i.lists$e[ ,c(1,3)]
e_dfa <- cbind(e_df[1:5, ], e_df[6:10, ], e_df[11:15, ])

kable(e_dfa, "latex", alig = "l",  caption = "List of environment items", booktabs = T) %>%
  kable_styling(latex_options = c("hold_position", "scale_down"))
```


### Items by type

```{r, layout="l-body-outset", warning=FALSE, echo=FALSE, message=FALSE}
c_dft <- as.data.frame(table(c_df$`sub-cat`))
names(c_dft) <- c("item", "count")
c_dft$percent <- round( (c_dft$count/sum(c_dft$count) * 100), digits =1)

kable(c_dft, "latex", alig = "l",  caption = "Type of consumer packaged goods", booktabs = T) %>%
  kable_styling(latex_options = c("hold_position"))

u_dft <- as.data.frame(table(u_df$`sub-cat`))
names(u_dft) <- c("item", "count")
u_dft$percent <- round((u_dft$count/sum(u_dft$count) * 100), digits =1)

kable(u_dft, "latex", alig = "l",  caption = "Type of utensils", booktabs = T) %>%
  kable_styling(latex_options = c("hold_position"))

e_dft <- as.data.frame(table(e_df$`sub-cat`))
names(e_dft) <- c("item", "count")
e_dft$percent <- round((e_dft$count/sum(e_dft$count) * 100), digits =1)

kable(e_dft, "latex", alig = "l",  caption = "Type of environment items", booktabs = T) %>%
  kable_styling(latex_options = c("hold_position"))

```

### Duration recipes

```{r, layout="l-body-outset", warning=FALSE, echo=FALSE, message=FALSE}
t_df <- time.list
names(t_df)[1:2] <- c("session", "regular")

kable(t_df, "latex", alig = "l", caption = "Duration of recipes", booktabs = T) %>%
    kable_styling(latex_options = c("hold_position"))
```

### Items used 

The list of the items used

```{r, layout="l-body-outset", warning=FALSE, echo=FALSE, message=FALSE}
total_df<- num.list$n.total
total_df$session[2] <- "regular"

kable(total_df, "latex", alig = "l", caption = "Total number of items used in minutes", booktabs = T) %>%
    kable_styling(latex_options = c("hold_position")) %>%
    footnote(symbol = ("c = CPGs, u = utensils, e = environment"))
```

### Total number of different items used 

The total number of different items used were as follows: 

```{r, layout="l-body-outset", warning=FALSE, echo=FALSE, message=FALSE}
total_df<- num.list$n.total
total_df$session[2] <- "new"

kable(total_df, "latex", alig = "l", caption = "Total number of different items used", booktabs = T) %>%
  kable_styling(latex_options = c("hold_position")) %>%
   footnote(symbol = ("c = CPGs, u = utensils, e = environment"))
```