---
title: "Results"
author: ''
date: ''
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r load myData, include=FALSE, echo=FALSE}
load("fname.RData")
```
### Participants

```{r, layout="l-body-outset", warning=FALSE, echo=FALSE, message=FALSE}
recipes_df <- recipe.list[, 1:3]
names(recipes_df)[1:2] <- c("session", "regular")

# required libraries
library(knitr)
library(kableExtra)
library(dplyr)

kable(recipes_df, alig = "l", caption = "List of recipes") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), "striped", full_width = FALSE)
```



An introduction to results. 
A description of each one of the results.

### Number of different items used 

The total number of different items used were as follows: 


```{r, layout="l-body-outset", warning=FALSE, echo=FALSE, message=FALSE}
total_df<- num.list$n.total
total_df$session[2] <- "regular"

kable(total_df, alig = "c", caption = "Total number of different items used") %>%
  kable_styling("striped", full_width = FALSE) %>%
   footnote(symbol = ("c = CPGs, u = utensil, e = environment"))
```



Here a description of this section. 

Insert table

Insert figures

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```


```
knitr::kable(
  mtcars[1:6, 1:6], caption = 'A subset of mtcars.'
)

Table Header  | Second Header
------------- | -------------
Table Cell    | Cell 2
Cell 3        | Cell 4 


To get `knitr` to present the results of a table, add `results="asis"` to the brackets to start the R code chunk. The ensuing output will look like this (though the table may come on the next page).

```


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
